Energy and the CES production function

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including horizontal line at 0.0.

@@

<<ResidualPlotFunction>>=
residualPlot <- function(data, withEnergyShape = 0){
  ggplot() +
    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
    scale_shape_manual(values=c(1, withEnergyShape)) +
    scale_size_manual(values=c(4,4)) +
    facet_grid(Country ~ flavor) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xlab("") +
    ylab("r") + 
    xy_theme() +
    theme(legend.title=element_blank())
}
@

>>>>

# Change variable names to make a nicer-looking graph
histDataForGraph$variable <- plyr::mapvalues(histDataForGraph$variable,
                                             from=c("iGDP", 
                                                    "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
                                                    "iL", "ihLest",
                                                    "iXpMP", "iXp", "iUMP", "iU"),
                                             to=c("y", 
                                                  "k", "k", "k", "k",
                                                  "l", "l",
                                                  "e", "e", "e", "e"))

@@

<<ResidualPlotFunction>>=
residualPlot <- function(data, withEnergyShape = 0){
  ggplot() +
    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
    scale_shape_manual(values=c(1, withEnergyShape)) +
    scale_size_manual(values=c(4,4)) +
    facet_grid(Country ~ flavor) +
    # geom_hline(aes(yintercept = 0), colour="gray50", size=0.1) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xlab("") +
    ylab("r") + 
    xy_theme() +
    theme(legend.title=element_blank())
}
@
